XOR-Some Prolific Pilot 3

### 2021-11-10 analysis/pilots/xor-some-prolific-pilot3.Rmd
refactor

## Checks & Exclusions
```{r data, results='hide', include=FALSE}
d <- read_csv("../data/pilots/results_63_xor-some-Prolific-pilot3_N50.csv")
```

@@

Get the vignettes and dimensions that were strongly deviating from expectations in the previous pilot and still did not improve:
```{r}
deviating_item_pilot2 <- read_csv("../data/pilots/pilot2_byItem_rating_deviations.csv") %>% select(-mean_deviation)
d_critical_deviations %>% select(-mean_deviation) %>% semi_join(., deviating_item_pilot2)
```

@@

d_long_plot_pilot2 <- read_csv("../data/pilots/pilot2_byItem_plotting.csv") %>% 
  mutate(pilot = "old")
# only keep data for those items that were also tested in the current pilot
d_long_plot_pilot2 <- semi_join(d_long_plot_pilot2, d_long_plot_full, by = c("title"))

>>>>

## Checks & Exclusions
```{r data, results='hide', include=FALSE}
d <- read_csv("../../data/pilots/results_63_xor-some-Prolific-pilot3_N50.csv")
```

@@

Get the vignettes and dimensions that were strongly deviating from expectations in the previous pilot and still did not improve:
```{r}
deviating_item_pilot2 <- read_csv("../../data/pilots/pilot2_byItem_rating_deviations.csv") %>% select(-mean_deviation)
d_critical_deviations %>% select(-mean_deviation) %>% semi_join(., deviating_item_pilot2)
```

@@

d_long_plot_pilot2 <- read_csv("../../data/pilots/pilot2_byItem_plotting.csv") %>% 
  mutate(pilot = "old")
# only keep data for those items that were also tested in the current pilot
d_long_plot_pilot2 <- semi_join(d_long_plot_pilot2, d_long_plot_full, by = c("title"))
